---
title: "2019-10-09"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r basic setup, message=FALSE, echo=F, eval=T}
library(dplyr); library(stringr); library(ggplot2); library(plotly); library(lubridate); library(readr); library(tidyr); library(showtext); library(colorspace); library(scales); library(magick); library(sf); library(rmapshaper); library(osmdata); library(plotly); library(leaflet); 
font_add("QYuan","cwTeXQYuan-Medium.ttf") # 新增字體
showtext_auto(enable=TRUE) #啟用字體
theme_set(theme_classic())
knitr::opts_chunk$set(fig.align='center', fig.showtext=T)
source("https://www.dropbox.com/s/mdx4777ugnluspz/webApplications.R?dl=1",encoding = "utf-8")
```

```{r}
webapp_project_create(dirlib = "./1225",overwrite = T)

```

```{r}
#poster1 三活動類型次數
```{r}
poster1 <- data.frame(
  type=c("青銀共賞電影","北大玩具節","聖誕點燈暨北大管樂節"),
  value=c(
    sum(poster$`event title`=="青銀共賞電影"),
    sum(poster$`event title`=="北大玩具節"),
    sum(poster$`event title`=="聖誕點燈暨北大管樂節"))
)
```
#faceboo1 三活動類型次數
```{r}
facebook1 <- data.frame(
  type=c("青銀共賞電影","北大玩具節","聖誕點燈暨北大管樂節"),
  value=c(
    sum(facebook$`event title`=="青銀共賞電影"),
    sum(facebook$`event title`=="北大玩具節"),
    sum(facebook$`event title`=="聖誕點燈暨北大管樂節"))
)
```
#website1 三活動類型次數
```{r}
website1 <- data.frame(
  type=c("青銀共賞電影","北大玩具節","聖誕點燈暨北大管樂節"),
  value=c(
    sum(website$`event title`=="青銀共賞電影"),
    sum(website$`event title`=="北大玩具節"),
    sum(website$`event title`=="聖誕點燈暨北大管樂節"))
)
```
```

