---
title: "UFO活動觸及高達百次"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    social: menu
    source_code: embed
---
```{r}
library(flexdashboard)
library(readr)
library(tidyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(magrittr)
library(showtext)
library(grDevices)
library(scales)
library(colorspace)
```


```{r}
load("HW8Data.Rda")
load("HW8Plot.Rda")
```

Column {data-width=600, data-height=500}
-------------------------------------
    
### 本學期三大活動
    
```{r}
graphList$totalT
```

### QRcode

<div id="北大玩具節"></div>


```{r,fig.width=2, fig.height=2}
graphList$toy 
graphList$movie
graphList$lalala
```



Column {.tabset data-width=400}
-------------------------------------
   
### Poster

```{r}
graphList$posterT
```   
 
### Facebook
    
```{r}
graphList$facebookT
```

### Website

```{r}
graphList$websiteT
```

<script type="text/javascript">
  $(window).bind("load",function(){
  var listenarea=document.querySelector("#qrcode > div.chart-stage.chart-stage-flex > div > p > img:nth-child(1)")
var listenarea1=document.querySelector("#qrcode > div.chart-stage.chart-stage-flex > div > p > img:nth-child(2)")
var listenarea2=document.querySelector("#qrcode > div.chart-stage.chart-stage-flex > div > p > img:nth-child(3)")
var actionarea=document.getElementById('北大玩具節')

function giveNews(){
    actionarea.innerHTML="北大玩具節"
}

listenarea.addEventListener("mouseover",giveNews)

function giveNews2(){
    actionarea.innerHTML="青銀共享電影"
}

listenarea1.addEventListener("mouseover",giveNews2)

function giveNews3(){
    actionarea.innerHTML="聖誕點燈暨北大管樂節"
}

listenarea2.addEventListener("mouseover",giveNews3)
  })
</script>